Visualization and analysis of probability distributions of large temporal data

### 2021-11-19 Rmd/05-conclusion.Rmd
Typos and consistent notation

The R package `hakear` (https://github.com/Sayani07/hakear) provides tools for selecting and sorting significant cyclic granularities. The function `wpd()` computes the weighted pairwise distances ($wpd$) for each cyclic granularity or pair of granularities, and the function `select_harmonies()` chooses those with significant patterns and ranks them from highest to lowest $wpd$. This package is reliant on parallel processing using multiple multi-core computers for faster computation of $wpd$. The selected harmonies can be plotted using package `gravitas` for potentially interesting displays. Currently, `hakear` implements ideas presented in Chapter \@ref(ch-hakear), but it will be integrated with `gravitas` in the future to explore distributions of a smaller number of time series.

@@

### Computational resources
Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches in Chapter \@ref(ch-hakear). In Chapter \@ref(ch-gracsr), our methods were tested on several data designs with different parameters to evaluate their performance. $wpd$ is computationally heavy for cyclic granularities with smaller levels. JS and WPD approaches are also computationally intensive when run on large number of customers. Hence, most of the scripts used to run these studies use parallel processing for better computational speed. R version 4.0.1 (2020-06-06) is utilized on the platform x86 64-apple-darwin17.0 (64-bit) operating on macOS Mojave 10.14.6, as well as the High Performance Computing (HPC) resources provided by [MonARCH](https://docs.monarch.erc.monash.edu/MonARCH/aboutMonArch.html).

@@

We address few limitations of the current framework that might serve as natural next steps for this work and some potential short- and long-term aims in future ideas.

@@

The time series are observed over a short period of time (1-3 years) in the motivating example of this research. Hence, they are assumed to be stationary. But it is possible that the distributions change over time, even over a short period. For the smart meter example, the distribution for a customer moving to a different house or changing electrical equipment may change drastically. To detect these dynamic changes, non-stationarity in time series has to be incorporated while visualizing distributions and also computing distances for two non-stationary time series or one stationary and another non-stationary time series.

@@

Another possible direction is to reduce computational time so that the proposed methods are easily scalable to many customers. The distance measure, $wpd$ is computationally heavy even under parallel computation. Moreover, while computing distances between time series, the proposed methods compute all possible pairwise distances, which acts as a computational barrier. Faster nearest-neighbor search algorithms can be employed here to decrease the computational load.

>>>>

The R package `hakear` (https://github.com/Sayani07/hakear) provides tools for selecting and sorting significant cyclic granularities. The function `wpd()` computes the weighted pairwise distances ($\wpd$) for each cyclic granularity or pair of granularities, and the function `select_harmonies()` chooses those with significant patterns and ranks them from highest to lowest $\wpd$. This package is reliant on parallel processing using multiple multi-core computers for faster computation of $\wpd$. The selected harmonies can be plotted using package `gravitas` for potentially interesting displays. Currently, `hakear` implements ideas presented in Chapter \@ref(ch-hakear), but it will be integrated with `gravitas` in the future to explore distributions of a smaller number of time series.

@@

### Computational resources
Simulation studies were carried out to study the behavior of $\wpd$, build the normalization method as well as compare and evaluate different normalization approaches in Chapter \@ref(ch-hakear). In Chapter \@ref(ch-gracsr), our methods were tested on several data designs with different parameters to evaluate their performance. $\wpd$ is computationally heavy for cyclic granularities with smaller levels. JS and WPD approaches are also computationally intensive when run on large number of customers. Hence, most of the scripts used to run these studies use parallel processing for better computational speed. R version 4.0.1 (2020-06-06) is utilized on the platform x86 64-apple-darwin17.0 (64-bit) operating on macOS Mojave 10.14.6, as well as the High Performance Computing (HPC) resources provided by [MonARCH](https://docs.monarch.erc.monash.edu/MonARCH/aboutMonArch.html).

@@

We address several limitations of the current framework that might serve as natural next steps for this work and some potential short- and long-term aims in future ideas.

@@

The time series are observed over a short period of time (1--3 years) in the motivating example of this research, and they are assumed to be stationary. But it is possible that the distributions change over time, even over a short period. For the smart meter example, the distribution for a customer moving to a different house or changing electrical equipment may change drastically. To detect these dynamic changes, non-stationarity in time series has to be incorporated while visualizing distributions and also computing distances for two non-stationary time series or one stationary and another non-stationary time series.

@@

Another possible direction is to reduce computational time so that the proposed methods are easily scalable to many customers. The distance measure, $\wpd$ is computationally heavy even under parallel computation. Moreover, while computing distances between time series, the proposed methods compute all possible pairwise distances, which acts as a computational barrier. Faster nearest-neighbor search algorithms can be employed here to decrease the computational load.
